% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Siddhesh Poyarekar}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{https://siddhesh.in}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Email: & \href{mailto:siddhesh@gotplt.org}{\tt siddhesh@gotplt.org} \\
    Homepage: & \href{https://siddhesh.in}{\tt https://siddhesh.in} \\
  \end{tabular}
\end{minipage}
\\ \\ \\ \\
I am a programmer with a deep interest in systems programming with a focus on Free and Open Source Software.

\section*{Employment}

\begin{itemize}
	\item {\tt Linaro Limited, 2015 - 2020}\\
		Served as technical lead of a toolchain team and contributed
		code to a number of FOSS projects ranging from the GNU
		toolchain to luajit, scipy and numpy.  Did extensive work in
		Arm architecture extension enablement and GNU toolchain
		optimisation for Arm server CPUs.
	\item {\tt Red Hat, 2009 - 2015}\\
		Part of the GNU toolchain team, maintaining glibc upstream, in
		Fedora and in RHEL.
	\item {\tt Tata Consultancy Services, 2006 - 2009}\\
		Developed code for trading and settlement systems for leading
		financial institution affiliated to the Government of India.
\end{itemize}

\section*{Open Source Projects}

\begin{itemize}
	\item \href{https://www.gnu.org/s/libc}{\tt GNU C Library}: Maintainer.
		Contributed various fixes and features.
	\item \href{https://www.gnu.org/s/gcc}{\tt GNU Compiler Collection}:
		Write after approval commiter.  Contributed fixes and
		performance improvement patches for aarch64.
	\item \href{https://www.gnu.org/s/binutils}{\tt GNU Debugger and Binutils}:
		Write after approval commiter. Contributed various fixes.
	\item \href{https://github.com/moonjit/moonjit}{moonjit}: A fork of the
		now inactive LuaJIT project.  Attempted to reboot project when
		it went inactive and contributed some bug fixes and provided
		package updates to Fedora.  The project is dormant again due to
		lack of time and interest.
	\item \href{https://fedora.org}{Fedora}: Maintain some packages.
	\item \href{https://www.openhub.net/accounts/siddhesh}{My OpenHUB
		Profile} has a list of a number of one-off contributions I have
		made to a variety of projects.
\end{itemize}

\section*{Education}

\begin{itemize}
  \item Masters in Computer Application, Mumbai University, 2006.
  \item Bachelor of Science, Computer Science, 2003.
\end{itemize}
\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
